{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2015-01-28 brains-protocol.tex
Clarify footnote on numbers of words per feature

The final set of variables we consider, as well as their cross-correlations, can be seen in Figure~\ref{fig:feature-corrs-filtered}.

>>>>

The final set of variables we consider, as well as their cross-correlations, can be seen in Figure~\ref{fig:feature-corrs-filtered}.\footnote{Note that since the final features stem from different datasets, they do not always encode the same words nor the same number of words.
Indeed, frequency encodes about 22.6k words, age of acquisition 30.1k words, number of phonemes 123.4k words, number of synonyms 111.2k, and clustering coefficient 5.7k words.
Quite often then, words from our dataset are encoded in only a subset of the features we use (if any at all); this is not a problem however, since the analysis is done on a per-feature basis and does not need words to be encoded in all the features at once.}
